\documentclass[a4paper,11pt,oneside,openany, report]{jsbook}
% \documentclass[11pt, a4paper, papersize, dvipdfmx]{jsarticle}
% \documentclass{jsarticle}
% \documentclass[fleqn, 11pt]{jsarticle}
%
\usepackage[top=20mm, bottom=20mm, left=25mm, right=25mm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{bm}
% \usepackage{graphicx}
\usepackage[dvipdfmx]{graphicx}
\usepackage{subfigure}
\usepackage{verbatim}
\usepackage{wrapfig}
\usepackage{ascmac}
\usepackage{makeidx}
\usepackage{cite}
\usepackage{times}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{here}
\usepackage{latexsym}
\usepackage{bm}
\usepackage{url}
\usepackage{amsfonts}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{afterpage}
\usepackage{caption}
\captionsetup[figure]{format=plain, labelformat=simple, font=normalsize}
\captionsetup[table]{format=plain, labelformat=simple, font=normalsize}

%
\makeindex
%
\setlength{\textwidth}{\fullwidth}
% \setlength{\textheight}{40\baselineskip}
% \addtolength{\textheight}{\topskip}
% \setlength{\voffset}{1.55in}
%
\newcommand{\diff}{\mathrm{d}}  %微分記号
\newcommand{\divergence}{\mathrm{div}\,}  %ダイバージェンス
\newcommand{\grad}{\mathrm{grad}\,}  %グラディエント
\newcommand{\rot}{\mathrm{rot}\,}  %ローテーション
\renewcommand{\prechaptername}{ }
\renewcommand{\postchaptername}{ }
\newcommand{\argmax}{\mathop{\rm arg~max}\limits}
\newcommand{\argmin}{\mathop{\rm arg~min}\limits}
\newcolumntype{Y}{>{\centering\arraybackslash}X} %中央揃え
\newcolumntype{Z}{>{\raggedleft\arraybackslash}X} 
%




\title{深層学習を用いた脳波信号からの運動意図推定}
\author{佐野\ \ 光 \\ Sano\ \ Hikaru}
% \author{Hikaru\ \ Sano}
\date{\today}


\begin{document}
%


%
\maketitle
%
%
\frontmatter
%%
% \addcontentsline{toc}{chapter}{はじめに}
% \include{abstract}
\setcounter{tocdepth}{2}
\tableofcontents
%
%
\mainmatter
%input 終了後改ページなし
%include 終了後改ページあり
\include{math_rule}

\chapter{研究背景}
\input{chapter/chapter1/INTRO}

\chapter{BCIのための要素技術}
\input{chapter/chapter2/FEATURE}
\input{chapter/chapter2/SIGNAL}
\input{chapter/chapter2/BSS}
\input{chapter/chapter2/Discriminant}

\chapter{従来の運動想起型BCI}
\input{chapter/chapter2/CSP}
\input{chapter/chapter2/oldSOTA}

\chapter{提案手法}
\input{chapter/chapter3/NN}

\chapter{実験と結果}

\chapter{結論と考察}
%
%
\appendix
%
\include{appendix}
%
%
\chapter*{謝辞}
% \addcontentsline{toc}{chapter}{謝辞}
...
...


\begin{thebibliography}{99}
  \bibitem{csssp} Guido Dornhege, Benjamin Blankertz, Matthias Krauledat, Florian Losch, Gabriel Curio, Klaus-Robert M?ller,
      ``Combined optimization of spatial and temporal
      filters for improving Brain-Computer Interfacing
      '',
      {\it IEEE TRANSACTIONS ON BIOMEDICAL ENGINEERING},
      Vol. XX,
      No. Y,
      2006.

  \bibitem{fbcsp} Kai Keng Ang, Zheng Yang Chin, Haihong Zhang, Cuntai Guan
      ``Filter Bank Common Spatial Pattern (FBCSP) in Brain-Computer Interface'',
      {\it IEEE TRANSACTIONS ON BIOMEDICAL ENGINEERING},
      {\it in Proc. 2008 Int. Joint Conf. Neural Netw.},
      pp. 2390-2397,
      2008.

  \bibitem{deepconv} Robin Tibor Schirrmeister,
      Jost Tobias Springenberg,
      Lukas Dominique Josef Fiederer,
      Martin Glasstetter,
      Katharina Eggensperger,
      Michael Tangermann,
      Frank Hutter,
      Wolfram Burgard,
      ``Deep learning with convolutional neural networks for EEG decoding and visualization'',
      {\it Human Brain Mapping},
      Vol. 38,
      No. 11,
      pp. 5391-5420,
      2017.
\end{thebibliography}
%
%
% \include{reference_acknowledgment}
%
%
\newpage
\printindex
%
%
\end{document}
